Young children rationally integrate semantic and pragmatic information sources to infer the meaning of words

### 2020-09-02 paper/manuscript.Rmd
draft for paper 2

## Predicting information integration accross development

@@

The *no word knowledge model* uses the same model architecture as the rational integration model. It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge. The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information. Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent. As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources. Finally, according to the *no speaker inforamtiveness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance. As a consequence, the inference is solely based on common ground expectations.

@@

A more detailed description of the experiments and the models can be found in the supplementary material. The experimental procedure, sample size and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations). Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin). Experiment 1 and 2 were designed to estimate children's developing sensitivity to each information source. Their results inform he parameter values in the model (see Fig. 1 c-f). Experiment 3 was designed to test how children integrate the different information sources.

@@

All participants were recruited from the floor of a Children’s museum in San José, California, USA. This population is characterized by diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status. Parents consented to their children’s participation and provided demographic information. All experiments were approved by the Stanford Institutional Review Board (protocol no. 19960).

@@

Experiment 2 tested children's sensitivity to common ground that is build up over the course of a conversation. In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two]. The general setup was the same as in Experiment 1 (Fig. S1b). The speaker was positioned between the tables. There was an unfamiliar object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second unfamiliar object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1. The positioning of the unfamiliar object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of unfamiliar objects. We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.

@@

As noted above, the explanation models used parameters that were additionally constrained by the data from Experiment 3. This had no effect on the way these parameters were combined in the rational integration model. The biased integration model is defined as $P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)$ with $P_{ME}$ representing a mutual exclusivity inference which takes in speaker inforamtiveness and object specific semantic knowledge. This inference is then weighted by the parameter $\phi$ and added to the respective prior probability, which is weighted by $1-\phi_i$. Thus, $\phi$ represents the bias in favor of the mutual exclusivity inference. In the developmental bias model the parameter $\phi$ is made to change with age ($\phi_i$) and the model is thus defined as $P^{dev\_bias}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i)$.

>>>>

## Predicting information integration across development

@@

The *no word knowledge model* uses the same model architecture as the rational integration model. It takes in expectations about speaker informativeness and common ground, but omits semantic knowledge that is specific to the familiar objects (i.e., uses only general semantic knowledge). That is, the model assumes a listener whose inference does not vary depending on the particular familiar object but only depends on the age specific average semantic knowledge. The *no common ground model* takes in object specific semantic knowledge and speaker informativeness but ignores common ground information. Instead of assuming that one object has a higher prior probability to be the referent because it is new in context, the speaker thinks that both objects are equally likely to be the referent. As a consequence, the listener does not differentiate between situations in which common ground is aligned or in conflict with the other information sources. Finally, according to the *no speaker informativeness model*, the listener does not assume that the speaker is communicating in an informative way and hence ignores the information provided by the utterance. As a consequence, the inference is solely based on common ground expectations.

@@

A more detailed description of the experiments and the models can be found in the supplementary material. The experimental procedure, sample size and analysis for each experiment were pre-registered (https://osf.io/7rg9j/registrations). Experimental procedures, model and analysis scripts can be found in an online repository (https://github.com/manuelbohn/spin). Experiment 1 and 2 were designed to estimate children's developing sensitivity to each information source. Their results inform the parameter values in the model (see Fig. 1 c-f). Experiment 3 was designed to test how children integrate the different information sources.

@@

All participants were recruited from the floor of a Children’s museum in San José, California, USA. This population is characterized by a diverse ethnic background (predominantly White, Asian, or mixed ethnicity) and high levels of parental education and socioeconomic status. Parents consented to their children’s participation and provided demographic information. All experiments were approved by the Stanford Institutional Review Board (protocol no. 19960).

@@

Experiment 2 tested children's sensitivity to common ground that is built up over the course of a conversation. In particular, we tested whether children keep track of which object is new to a speaker and which they have encountered previously [@akhtar1996role; @diesendruck2004two]. The general setup was the same as in Experiment 1 (Fig. S1b). The speaker was positioned between the tables. There was an unfamiliar object (drawn for the purpose of the study) on one of the tables while the other table was empty. Next, the speaker turned to one of the tables and either commented on the presence ("Aha, look at that.") or the absence ("Hm, nothing there") of an object. Then the speaker disappeared. While the speaker was away, a second unfamiliar object appeared on the previously empty table. Then the speaker returned and requested an object in the same way as in Experiment 1. The positioning of the unfamiliar object in the beginning of the experiment, the speaker as well as the location the speaker turned to first was counterbalanced. Children received five trials, each with a different pair of unfamiliar objects. We coded as correct choice if children chose the object that was new to the speaker as the referent of the novel word.

@@

As noted above, the explanation models used parameters that were additionally constrained by the data from Experiment 3. This had no effect on the way these parameters were combined in the rational integration model. The biased integration model is defined as $P^{biased}_{L_1}(r \mid u; \{\phi, \rho_i, \alpha_i, \theta_{ij} \}) = \phi \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi) \cdot P(r \mid \rho_i)$ with $P_{ME}$ representing a mutual exclusivity inference which takes in speaker informativeness and object specific semantic knowledge. This inference is then weighted by the parameter $\phi$ and added to the respective prior probability, which is weighted by $1-\phi_i$. Thus, $\phi$ represents the bias in favor of the mutual exclusivity inference. In the developmental bias model the parameter $\phi$ is made to change with age ($\phi_i$) and the model is thus defined as $P^{dev\_bias}_{L_1}(r \mid u; \{\phi_i, \rho_i, \alpha_i, \theta_{ij} \}) = \phi_i \cdot P_{ME}(r \mid u; \{\alpha_i, \theta_{ij}\})  + (1-\phi_i)$.
